Meta analysis of reprocessed RNASeq data from AMP-AD (all 6 brain regions)

### 2019-11-25 code/metaAnalysisForDiffExp_NoCBE.Rmd
Add NoCBE

>>>>

parentId = 'syn18936948';
activityName = 'Meta analysis of differential expression (No CBE)';
activityDescription = 'Fixed and random effect meta-analysis of AMP-AD data (all 6 brain regions)';
thisFileName <- 'metaAnalysisForDiffExp_NoCBE.Rmd'
# Github link
thisRepo <- getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
